Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Add CI support to contributions
Add TBDs to section "Problem"
Add a TBD note

@@

@@

\begin{itemize}
\item The Haskell community does not have common syntax to describe
examples/properties with Haddock markup syntax.
\item The Haskell community does not have a BDD tool for examples/properties
    for users.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidence as code documentation}
\label{sec:for-developers}

>>>>

\item
    Improve CI support for \doctest{} and \hspec{}

    TBD:
    \emph{This relates to hspec-discover and Doctest's Cabal support.}

@@

\begin{quote}
    TBD:
\begin{itemize}
    \item Motivate \verb|test-shouldbe|
    \item Motivate \verb|shouldThrow|
    \item \emph{optional:} Motivate why it's important to integrate \doctest{} with
        Cabal.
    \item \emph{optional:} Motivate \verb|hspec-discover|
\end{itemize}
\end{quote}

@@

\begin{itemize}
\item
    The Haskell community does not have common syntax to describe
    examples/properties with Haddock markup syntax.
\item
    The Haskell community does not have a BDD tool for
    examples/properties for users.
\item
    Hspec does not provide combinators to express expectations with
    BDD terminology
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidence as code documentation (TBD: Is this still
appropriate here?}
\label{sec:for-developers}
